Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-10 Paper/paper.tex
only partway through background

\newcommand{\toolname}{{\textcolor{blue}TOOL\_NAME }}
\newcommand{\Ben}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

@@

The AS-layer of the Internet is the highest level of organization of the Internet. ASes generally represent ISP networks,
large university networks, or government entities. Interdomain routing between these ASes is governed by BGP, and
individual ASes may have local preferences for how they wish to send packets along, but they cannot govern the paths
selected by other ASes. AS topology researchers often use measurement tools to create a picture of the global Internet.
These measurement tools, for instance BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}.
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.

>>>>

\newcommand{\toolname}{{\textcolor{blue}TOOL\_NAME }}
\newcommand{\Ben}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommand{\Steph}[2][1=]{\todo[linecolor=yellow,backgroundcolor=yellow!25,bordercolor=yellow,#1]{#2}}

@@

The AS-layer is the highest level of organization of the Internet, with each individual AS consisting of a separately administered network, which could represent a large ISP, a university network, or a government entity. The Border Gateway Protocol (BGP) is used to route traffic among ASes. \Steph[inline]{need citations}.  AS-level routes are known as \emph{paths} and are specified by routing tables stored locally in each BGP node.  These tables express local preferences for how data are routed, e.g., if there are multiple paths to a single destination, an AS may prefer the path that costs the least.

Because BGP is a distributed protocol, with all connectivity
information stored in the local routing tables, it is challenging to
infer the exact AS topology at any point in time.  There are several
strategies for inferring the AS graph from local information, and no method is perfect.  
BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}.\Steph[inline]{Kirts: Please explain BGPStream and what the problem with it is.}
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.
